DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-29 paper/evaluation.tex
Minor change to evaluation section

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in 
\ref{fig:palloc_bandwidth_exectime}. With zero or one co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
However, we find that with two or more co-runners, DNN performance becomes
worse. In the case of two co-runners, average control loop time increases
by 66.31 ms, or 26\%, and with three co-runners, the average time
is 265.64 ms, of 49\%, greater.

%TODO: Talk about the prefetcher, or something, for why the benchmark performance is worse.

>>>>

Finally, we run a single model alongside memory intensive co-runners 
again, but ensure that each task is given equal amounts of L2 cache space.
For this, we assign two colors to each task, regardless of the number of
tasks being scheduled. As a result, the entire cache is not utilized in
experiments with less than four tasks. The results can be seen in 
\ref{fig:palloc_bandwidth_exectime}. With zero or one co-runners, the DNN
performance doesnt't change relative to when the cache wasn't partitioned.
However, we find that with two or more co-runners, DNN performance becomes
worse. In the case of two co-runners, average control loop time increases
by 66.31 ms, or 26\%, and with three co-runners, the average time
is 265.64 ms, of 49\%, greater. This difference is most likely due to the
L2's prefetcher, which has the potential to generate additional memory
contention and, thus, affect the performance of the DNN.
At the same time, though, the L2 miss rates of the model don't correlate 
to the timing increases seen, as is shown in 
\ref{fig:palloc_bandwidth_l2missrate}. With partitioning enabled, L2 miss
rates are higher when no co-runners are present, which is expected, but 
are the same or lower when co-runners are introduced. If the model was 
sensitive to the L2 cache, then performance would have improved as 
proportionaly fewer L2 misses occurred. Since this is not the case, it 
can be seen that the DNN is more sensitive to the performance of the DRAM
controller, and not the shared L2 cache.
